%──────────────────────────────────────────────────────────────────────────────
% William Ortiz – DevSecOps Engineer Resume
%
% Compile with: pdflatex William_Ortiz_Resume.tex
% Requires:     texlive-latex-base, texlive-latex-extra, texlive-fonts-extra
%──────────────────────────────────────────────────────────────────────────────
\documentclass[11pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.65in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{fontawesome5}

% ── Colors ───────────────────────────────────────────────────────────────────
\definecolor{primary}{HTML}{800000}
\definecolor{darktext}{HTML}{1A1A1A}
\definecolor{graytext}{HTML}{555555}

% ── Hyperlinks ───────────────────────────────────────────────────────────────
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary,
    pdftitle={William Ortiz - DevSecOps Engineer Resume},
    pdfauthor={William Ortiz},
}

% ── Section Formatting ──────────────────────────────────────────────────────
\titleformat{\section}
    {\Large\bfseries\color{primary}}
    {}{0em}{}
    [\vspace{-0.5em}\textcolor{primary}{\rule{\textwidth}{1pt}}]

\titlespacing*{\section}{0pt}{1.2em}{0.6em}

% ── List Formatting ─────────────────────────────────────────────────────────
\setlist[itemize]{
    leftmargin=1.5em,
    itemsep=2pt,
    parsep=0pt,
    topsep=4pt,
    label=\textcolor{primary}{\textbullet}
}

% ── Spacing ─────────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% ── Custom Commands ─────────────────────────────────────────────────────────
\newcommand{\position}[4]{%
    \textbf{\large #1} \hfill \textcolor{graytext}{#2} \\
    \textit{\color{graytext}#3} \hfill \textit{\color{graytext}#4}
    \vspace{4pt}
}

\newcommand{\education}[4]{%
    \textbf{#1} \hfill \textcolor{graytext}{#2} \\
    \textit{\color{graytext}#3} \hfill \textit{\color{graytext}#4}
    \vspace{4pt}
}

%══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\Huge\bfseries\color{darktext} William Ortiz} \\[6pt]
    {\large\color{primary} DevSecOps Engineer} \\[10pt]
    \color{graytext}
    \faEnvelope\enspace \href{mailto:contact@williamortiz.dev}{contact@williamortiz.dev} \quad
    \faGlobe\enspace \href{https://williamortiz.dev}{williamortiz.dev} \quad
    \faGithub\enspace \href{https://github.com/WilliamOrtizDev}{WilliamOrtizDev} \quad
    \faLinkedin\enspace \href{https://www.linkedin.com/in/williamortizdev/}{williamortizdev}
\end{center}

\vspace{0.5em}

% ── Summary ─────────────────────────────────────────────────────────────────
\section{Professional Summary}

Dedicated DevSecOps Engineer with a strong background in system administration
and cybersecurity. Experienced in automating security practices throughout the
software development lifecycle, building secure CI/CD pipelines, managing cloud
infrastructure, and fostering a security-first culture. Skilled at integrating
security seamlessly to enable innovation rather than impede it.

% ── Skills ──────────────────────────────────────────────────────────────────
\section{Technical Skills}

\begin{tabularx}{\textwidth}{@{} l X @{}}
    \textbf{Cloud \& Infra}    & AWS, Docker, Kubernetes, Red Hat Linux \\[3pt]
    \textbf{Automation \& IaC} & Terraform, Ansible, Packer, GitLab CI/CD \\[3pt]
    \textbf{Languages}         & Python, Bash \\[3pt]
    \textbf{Security}          & IAM, Vulnerability Management, Network Security, SAST/DAST \\[3pt]
    \textbf{Other}             & Git, Project Management, Agile/Scrum, Incident Response
\end{tabularx}

% ── Experience ──────────────────────────────────────────────────────────────
\section{Professional Experience}

% TODO: Replace with actual positions
\position{DevSecOps Engineer}{Company Name}{City, State}{Month Year -- Present}
\begin{itemize}
    \item Designed and implemented secure CI/CD pipelines using GitLab CI, reducing deployment time by XX\% while integrating automated security scanning (SAST, DAST, container scanning).
    \item Managed cloud infrastructure on AWS using Terraform and Ansible, ensuring compliance with security best practices and organizational policies.
    \item Containerized applications with Docker and orchestrated with Kubernetes, implementing pod security policies and network policies.
    \item Conducted vulnerability assessments and remediation, reducing critical vulnerabilities by XX\% within the first quarter.
    \item Automated IAM policy management and access reviews, improving security posture and audit readiness.
\end{itemize}

\vspace{0.6em}

\position{Systems Administrator}{Company Name}{City, State}{Month Year -- Month Year}
\begin{itemize}
    \item Administered Red Hat Linux servers across production and staging environments, maintaining 99.9\% uptime.
    \item Implemented infrastructure-as-code practices using Ansible for configuration management across XX+ servers.
    \item Developed monitoring and alerting solutions, reducing mean time to detection (MTTD) for security incidents.
    \item Managed network security including firewall rules, VPN configurations, and intrusion detection systems.
\end{itemize}

% ── Projects ────────────────────────────────────────────────────────────────
\section{Notable Projects}

\textbf{Portfolio Website} \hfill \href{https://williamortiz.dev}{williamortiz.dev}
\begin{itemize}
    \item Built a responsive portfolio site with dynamic GitHub project loading, Resend API contact form integration, and full ADA/SEO compliance.
\end{itemize}

% TODO: Add more projects from GitHub or professional work

% ── Education ───────────────────────────────────────────────────────────────
\section{Education}

\textbf{Bachelor of Science in Computer Science} \hfill Western Governors University \\
\textbf{Bachelor of Science in Business Administration} \hfill Western Governors University

% ── Certifications ──────────────────────────────────────────────────────────
\section{Certifications}

\begin{itemize}
    \item Red Hat Certified System Administrator (RHCSA)
    \item Red Hat Certified Engineer (RHCE)
    \item HashiCorp Terraform Associate
    \item CompTIA Network+
    \item CompTIA Security+
\end{itemize}

\end{document}
